Papers

### 2024-06-04 papers.qmd
updates to slides and papers

## 2024
A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. submitted, 2023.

@@

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@

"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019

>>>>

## 2024
A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. accepted, 2023.

@@

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@

"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019 [Slides](https://jdtuck.github.io/presentations/FDA_Overview/FDA_Overview.html)
